Regime transition identification for water governance at a basin scale

### 2020-11-24 tex/main/manuscript.tex
update references

\label{introduction-section-1}
% 作为“人类世行星戏剧的中心”, water 不仅对地球系统进程至关重要，而且还支持着人类社会的发展。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for earth system processes, but also supporting development of human societies. 
%* add references
% 由于人类对水的依赖，人类活动深刻地改变了自然水循环，并逐步走向水-社会水循环。
Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle stage by stage
\cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
% 面对这一重大转型，世界上许多大流域作为经济和文明热点，迫切需要成功的可持续治理
Facing this major transformation, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful water governance for sustainability
\cite{bestAnthropogenicStressesWorld2019}. 
% 水治理作为地球系统治理框架的重要组成部分，需要对人与水之间复杂的关系有深刻的理解。
As an integral part of a proposed earth system governance framework, water governance requires deep understanding of the complex relationships between human and water.
% Biermann et al., 2012.
% 因此，识别流域尺度上由水-社会水循环转变引起的水治理变化至关重要。
Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, at a basin scale.

\label{introduction-section-2}
% 缺乏治理就是缺乏可持续性
Missing governance means missing sustainability.
% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
According to United Nations Development Programme (UNDP), three key dimensions are decided by water governance regime directly (see \textit{SI Appendix} Methods S1): ``How much water can be used? (supply)'', ``How to balances different water use services? (purpose)'' and ``How to allocate water equally and efficiently? (allocation)''.
% 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts 
\cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
Regime shifts, therefore, is a signal of substantive change of water governance and may lead to new challenges to sustainability.
% 然而，随着环境、经济、社会和政治方面的变革，水治理制度可以从上述每一个关键方面(供应、目的和分配)发生重大变化。
Along with environmental, economic, social and political changes, however, water governance regimes can substantially shift from each of the above key dimensions (supply, purpose, and allocation).
% 首先，受环境恶化和进一步经济增长对水的需求的影响，维持社会的水供应可能会因为缺水而面临压力，但治理政策(如修建水库)可能会有所帮助.
Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water supply for societies can face stress because of scarcity, but policies (such as construction of reservoirs and channels) can be helpful
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
Secondly, there is trade-off between provisioning-purpose water use (such as domestic use and food production uses) and non-provisioning-purpose water (such as uses for industrial production or energy), which in need of weights through water governance
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
Thirdly, since governance concerns water allocation at the whole basin, it not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by social and political changes.
% 综上所述，随着向以人为主导的水-社会水循环的转变，水治理制度由三个变化的维度(供应、目的和分配)决定，缺乏简单而全面的方法来确定制度变化，这对成功治理留下了关键的差距.
Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (supply, purpose and allocation). However, the lack of simple but comprehensive method to identify changes of water governance regime leaves fatal gaps towards successful water governance for sustainability (Figure~\ref{fig:framework}).

\label{introduction-section-3}
% 黄河流域(YRB，详见方法S2)经历了中国最密集的用水和剧烈的制度变迁，从古代起就面临着水资源管理方面的非凡挑战。
The Yellow River Basin (YRB, see \textit{Appendix} Methods S2 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges in water governance from the ancient time.
% 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
Half century ago, the huge sediment loads of the Yellow River not only brought disasters, but also made it difficult for water use. 
% 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these issues were effectively contained.
% 然而，由于过度用水，黄河的严重干涸带来了新的治理挑战，并推动了一系列相关政策(如调节用水和限制取水)来应对。
However, because of over water use, serious drying up of the Yellow River led new governance challenges and promoted a range of related policies (such as regulating water use and limiting water withdrawals) to deal with.
% 今天，由于水的需求仍然难以完全满足，各区域和部门之间必须进行各种权衡，要取得成功的水治理还有很长的路要走。
Today, as water demands are still difficult to be completely met and various trade-offs must be involved between regions and sectors, there is still a long way towards successful water governance.
% 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
All in all, the YRB has been the most rapid-changing basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors.
% 因此，确定YRB内的水管理制度变化可以为世界快速变化的大河流流域提供洞察，以应对可持续发展方面的挑战。
Therefore, identifying the regime shifts for water governance within YRB can provide insights to the world's rapid-changing big river basins for meeting challenges towards sustainability.

@@

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
	\caption{
		A framework for understanding the relationship between transformation towards hydro-social cycle and water governance regimes, with a main goal in detecting regime shifts by a simple and comprehensive index.
		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
		\textbf{A,} three key dimensions (supply, purpose and allocation) of water governance (see \textit{Appendix SI} Methods S4 for details). Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance. (2) ``purpose'' weighted between provisioning services or non-provisioning services. (3) ``allocation'' changes between balanced or lopsided. We presume that water governance regimes equally weighted by these basic dimensions. 
		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
		\textbf{B,} the governance changes combined the three dimensions. Because the above three dimensions change along with the trajectory towards hydro-social water cycle, combined water governance status is also various with that. When abrupt change occurs during this process, it may indicate a regime shift in water governance.
	}
	\label{fig:framework}
\end{figure*}

@@

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Causes of water governance regime shifts: environment changes, economic growths and efficiency changes, social transformation and water governance policies.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use intensity for unit production (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and water supply. These marked reservoirs, therefore are more significant for the entire basin, rather than regional development.
		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{Appendix SI} Table S2). Four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order.
	}
	\label{fig:Causes}
\end{figure}

@@

\begin{figure*}[htbp!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		\textbf{Transition schema of water governance.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. There is a transformation towards the hydro-social water cycle where red loop increases.
		\textbf{A. Natural phase:} As an indispensable provisioning-purpose resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional phase:} With further developed and economically efficient industries and services, trade-off between provisioning-purpose and non-provisioning-purpose water use becomes prominent. Rather than determined by local socio-economic systems any more, water withdrawals and management act as considerations within the entire basin more, therefore. 
		\textbf{D. Water governance challenges} Throughout the transition regimes, water governance faces primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
	}
	\label{fig:summary}
\end{figure*}

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
Our results show that three distinct but sequential governance regimes within YRB (massive supply regime (1965-1978), purpose turned regime (1979-1993) and all-sided governance regime (1994-2013)), whose shifts caused by different environmental, economic, social or political aspects.
% 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social water cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages (Figure~\ref{fig:summary}).

% 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
At the massive supply regime (1965-1978), since the basin economy was mainly dependent on agriculture and natural water resources were relatively abundant, water governance tended to supply more resources for agriculture (by construction of reservoirs and channels for examples). 
% 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
Due to the limited effects from socio-economic loops at this regime, water governance with few protective policies encouraged unlimited water supply for the required regions, with little consideration of the social equity and environmental impact over the basin. 
% 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
With nearly 80\% of surface water used mainly for provisioning-purpose, the Yellow River dried up at the second half of the regime. 
% 随着干旱化的日益严重，造成了湿地萎缩、生物多样性下降等生态问题，呈现出巨大的环境危机。
Ecological issues such as shrink of wetlands, declines of biodiversity emerged as the drying up became more and more serious, leading a huge crisis in environment which challenges water governance rigorously.

% “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
The start of ``the purpose turned regime'' (1978) coincided with Chinese ``reform and opening-up'', the huge social transformation led the emerging industry and services broke the dominance of agriculture and competed for water use. 
% 面对遗留的环境问题和全新的经济挑战，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
Facing legacy environmental challenges and new economic challenges, the Yellow River Conservancy Commission undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work regarding hydrology and basin management in YRB.
% 该制度稳态不仅遏止了用水效率低下的农业的扩张，更出台了一系列政策法规应对水资源压力，并调节用水分配。
As results, the YRB introduced new policies and regulations ahead of the whole country (for an example, ``the 87 Water Diversion Scheme'') to allocate water and successfully stopped the expansion of irrigated water consumption.

% 直到大约1993年以来，由于社会经济发展后先进技术的广泛应用，水资源利用效率有了显著提高，才出现了下一个政权向全面治理的转变。
The next regime shift to all-sided governance was not brought until a significant increase in water use efficiency since about 1993, due to the widely applying of advanced technologies after socio-economic developments. 
% 区域和部门之间在水需求方面的社会经济权衡在这一制度中发挥关键作用，因此水治理需要满足更全面、更有效率的水分配
Since socio-economic trade-offs between regions and sectors in water demands played a key role at this regime, water governance needs to meet efficient water allocating and balances between different purposes, under limited water supply.
% 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
For an example, the water rights conversion project popularized since this period may save regional agricultural water for industrial developments even in another region.
% 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
On the other hand, however, the old water policy (i.g. ``The 87 Water Diversion Scheme'') which once helped the YRB get rid of the environmental crisis, had become the shackle of social equity and coordinated allocation under the new regime because of path dependence.
% 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
Anyhow, myriad national-level water policies were proposed or adjusted under this regime, as the absence of such policies gaps and social injustice regarding water use are becoming new structural challenges for governance

% 总的来说，三个水治理稳态之间的先后转变，都是随着流域向社会-水循环发展的过程中先后发生的，存在明显的过渡趋势。
In general, shifts of the three governance regimes occurred sequentially along with a transformation towards the hydro-social cycle.
% 随着不断增强的人类压力在全球普遍逐渐占据主导，这种过渡趋势在社会-生态系统中被认为是普遍存在的，例如生态系统服务和国家经济-社会发展。
This kind of transition may be widespread in socio-ecological systems, such as transition of ecosystem services and transition of economic-social developments, as increasing anthropogenic impacts gradually change the world at large.
% 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
Regards to water governance we mainly concern, we find that the transition regimes echoes the two kinds of major water governance challenges globally (resource challenges and structural challenges).
% 以水资源短缺和供水困难为代表的资源挑战，主要是未开发和正在开发的流域所面临的，与经济和环境变化密切相关。
Resource challenges represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and highly related to economic and environmental changes. 
% 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
Other side, highly-controlled and developed basins (especially for cross-border rivers) are mainly facing structural challenges such as water disputes or lack of equity, and in urgent need of flexible and efficient governance structure for social and political aspects.
% 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
It is very representative that resource challenges and structural challenges have occurred successively along the transition of water governance within the YRB, because of rapid-changing regimes.
% 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
Based on that, our analysis suggests that the early stage of transition often leads resource challenges by economic and environmental changes, while the later stage is dominated by structural challenges regarding social and political aspects.
% 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
Aligned with the core dimensions emphasized by UNDP regarding water governance, this schema paints a co-evolution between the governance challenges and basins' transformation towards a hydro-social water cycle, again.

>>>>

\label{introduction-section-1}
% 作为“人类世行星戏剧的中心”, water 不仅对地球系统进程至关重要，而且还支持着人类社会的发展。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for earth system processes, but also supporting development of human societies. 
%* add references
% 由于人类对水的依赖，人类活动深刻地改变了自然水循环，并逐步走向水-社会水循环。
Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle stage by stage
\cite{gleeson2020,sivapalan2012,qin2014,abbott2019,levia2020}.
% 面对这一重大转型，世界上许多大流域作为经济和文明热点，迫切需要成功的可持续治理
Facing this major transformation, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful water governance for sustainability
\cite{bestAnthropogenicStressesWorld2019,falkenmark2019,dibaldassarre2019}. 
% 水治理作为地球系统治理框架的重要组成部分，需要对人与水之间复杂的关系有深刻的理解。
As an integral part of a proposed earth system governance framework, water governance requires deep understanding of the complex relationships between human and water
\cite{biermann2012,steffen2020,dibaldassarre2019}
% 因此，识别流域尺度上由水-社会水循环转变引起的水治理变化至关重要。
Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, at a basin scale.

\label{introduction-section-2}
% 缺乏治理就是缺乏可持续性
For water, missing governance means missing sustainability \cite{undpwatergovernancefacility2015}.
% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
According to United Nations Development Programme (UNDP), three key dimensions are decided by water governance regime directly: ``How much water can be used? (supply)'', ``How to balances different water use services? (purpose)'' and ``How to allocate water equally and efficiently? (allocation)'' 
\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
% 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts 
\cite{rocha2018,gregr2020}.
% 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
Regime shifts, therefore, can be a signal of substantive change of water governance and may lead to new challenges to sustainability 
\cite{steffen2020}.
% 然而，随着环境、经济、社会和政治方面的变革，水治理制度可以从上述每一个关键方面(供应、目的和分配)发生重大变化。
Along with environmental, economic, social and political changes, however, water governance regimes can substantially shift from each of the above key dimensions (supply, purpose, and allocation)
\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
% 首先，受环境恶化和进一步经济增长对水的需求的影响，维持社会的水供应可能会因为缺水而面临压力，但治理政策(如修建水库)可能会有所帮助.
Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water supply for societies can face stress because of scarcity, but policies (such as construction of reservoirs and channels) can be helpful
\cite{greveGlobalAssessmentWater2018, wada2017, qin2019}.
% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
Secondly, there is trade-off between provisioning-purpose water use (such as domestic use and food production uses) and non-provisioning-purpose water (such as uses for industrial production or energy), which in need of weights through water governance
\cite{liu2017, florke2018}.
% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
Thirdly, since governance concerns water allocation at the whole basin, it not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by social and political changes
\cite{roobavannan2017,speed2013}.
% 综上所述，随着向以人为主导的水-社会水循环的转变，水治理制度由三个变化的维度(供应、目的和分配)决定，缺乏简单而全面的方法来确定制度变化，这对成功治理留下了关键的差距.
Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (supply, purpose and allocation). However, the lack of simple but comprehensive method to identify changes of water governance regime leaves fatal gaps towards successful water governance for sustainability (Figure~\ref{fig:framework}).

\label{introduction-section-3}
% 黄河流域(YRB，详见方法S2)经历了中国最密集的用水和剧烈的制度变迁，从古代起就面临着水资源管理方面的非凡挑战。
The Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges in water governance from the ancient time.
% 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
Half century ago, the huge sediment loads of the Yellow River not only brought disasters, but also made it difficult for water use 
\cite{song2020,li2020}. 
% 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these issues were effectively contained 
\cite{wang2016,wu2020}.
% 然而，由于过度用水，黄河的严重干涸带来了新的治理挑战，并推动了一系列相关政策(如调节用水和限制取水)来应对。
However, because of over water use, serious drying up of the Yellow River led new governance challenges and promoted a range of related policies (such as regulating water use and limiting water withdrawals) to deal with 
\cite{xia2012}.
% 今天，由于水的需求仍然难以完全满足，各区域和部门之间必须进行各种权衡，要取得成功的水治理还有很长的路要走。
Today, as water demands are still difficult to be completely met and various trade-offs must be involved between regions and sectors, there is still a long way towards successful water governance 
\cite{wang2019, wohlfart2016}.
% 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
All in all, the YRB has been the most rapid-changing basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors 
\cite{bestAnthropogenicStressesWorld2019}.
% 因此，确定YRB内的水管理制度变化可以为世界快速变化的大河流流域提供洞察，以应对可持续发展方面的挑战。
Therefore, identifying the regime shifts for water governance within YRB can provide insights to the world's rapid-changing big river basins for meeting challenges towards sustainability.

@@

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
	\caption{
		A framework for understanding the relationship between transformation towards hydro-social cycle and water governance regimes, with a main goal in detecting regime shifts by a simple and comprehensive index.
		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
		\textbf{A,} three key dimensions (supply, purpose and allocation) of water governance (see Methods for details). Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance. (2) ``purpose'' weighted between provisioning services or non-provisioning services. (3) ``allocation'' changes between balanced or lopsided. We presume that water governance regimes equally weighted by these basic dimensions. 
		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
		\textbf{B,} the governance changes combined the three dimensions. Because the above three dimensions change along with the trajectory towards hydro-social water cycle, combined water governance status is also various with that. When abrupt change occurs during this process, it may indicate a regime shift in water governance
		\cite{steffen2018,abbott2019,levia2020}.
	}
	\label{fig:framework}
\end{figure*}

@@

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Causes of water governance regime shifts: environment changes, economic growths and efficiency changes, social transformation and water governance policies.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Appendix} Methods S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use intensity for unit production (WUI) respectively (\textit{SI Appendix} Methods S2).
		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and water supply. These marked reservoirs, therefore are more significant for the entire basin, rather than regional development.
		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{Appendix SI} Table S2). Four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{Appendix SI} Table S3).
	}
	\label{fig:Causes}
\end{figure}

@@

\begin{figure*}[htbp!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		\textbf{Transition schema of water governance.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. There is a transformation towards the hydro-social water cycle where red loop increases.
		\textbf{A.} As an indispensable provisioning-purpose resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B.} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C.} With further developed and economically efficient industries and services, trade-off between provisioning-purpose and non-provisioning-purpose water use becomes prominent. Rather than determined by local socio-economic systems any more, water withdrawals and management act as considerations within the entire basin more, therefore. 
		\textbf{D. Water governance challenges} Throughout the transition regimes, water governance faces primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
	}
	\label{fig:summary}
\end{figure*}

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
Our results show that three distinct but sequential governance regimes within YRB: massive supply regime (1965-1978), purpose turned regime (1979-1993) and all-sided governance regime (1994-2013), whose shifts caused by different environmental, economic, social or political aspects.
% 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social water cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages (Figure~\ref{fig:summary}).

% 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
At the massive supply regime (1965-1978), since the basin economy was mainly dependent on agriculture and natural water resources were relatively abundant (\textit{SI Appendix} Figure S3), water governance tended to supply more resources for agriculture (by construction of reservoirs and channels for examples). 
% 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
Due to the limited effects from socio-economic loops at this regime, water governance with few protective policies encouraged unlimited water supply for the required regions, with little consideration of the social equity and environmental impact over the basin 
\cite{zhou2020}. 
% 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
With nearly 80\% of surface water used mainly for provisioning-purpose, the Yellow River dried up at the second half of the regime (\textit{SI Appendix} Figure S10). 
% 随着干旱化的日益严重，造成了湿地萎缩、生物多样性下降等生态问题，呈现出巨大的环境危机。
Ecological issues such as shrink of wetlands, declines of biodiversity emerged as the drying up became more and more serious, leading a huge crisis in environment which challenges water governance rigorously.

% “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
The start of ``the purpose turned regime'' (1978) coincided with Chinese ``reform and opening-up'', the huge social transformation led the emerging industry and services broke the dominance of agriculture and competed for water use (Figure~\ref{fig:Causes}). 
% 面对遗留的环境问题和全新的经济挑战，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
Facing legacy environmental challenges and new economic challenges, the Yellow River Conservancy Commission undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work regarding hydrology and basin management in YRB 
\cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
% 在全国率先出台了新的政策法规(如“87调水方案”)进行调水，成功阻止了灌溉用水量的扩大。
As results, the YRB introduced new policies and regulations ahead of the whole country (for an example, ``the 87 Water Diversion Scheme'') to allocate water and successfully stopped the expansion of irrigated water consumption 
\cite{wang2018}.

% 直到大约1993年以来，由于社会经济发展后先进技术的广泛应用，水资源利用效率有了显著提高，才出现了下一个政权向全面治理的转变。
The next regime shift to all-sided governance was not brought until a significant increase in water use efficiency since about 1993, due to the widely applying of advanced technologies after socio-economic developments. 
% 区域和部门之间在水需求方面的社会经济权衡在这一制度中发挥关键作用，因此水治理需要满足更全面、更有效率的水分配
Since socio-economic trade-offs between regions and sectors in water demands played a key role at this regime, water governance needs to meet efficient water allocating and balances between different purposes, under limited water supply 
\cite{dalin2015a}.
% 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
For an example, the water rights conversion project popularized since this period may save regional agricultural water for industrial developments even in another region, while the water transfer is also another huge project to meet water needs within the YRB
\cite{barnett2015,yunpeng2010}.
% 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
On the other hand, however, the old water policy (i.g. ``The 87 Water Diversion Scheme'') which once helped the YRB get rid of the environmental crisis, had become the shackle of social equity and coordinated allocation under the new regime because of path dependence 
\cite{wang2018}.
% 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
Anyhow, myriad national-level water policies were proposed or adjusted under this regime, as the absence of such policies gaps and social injustice regarding water use are becoming new structural challenges for governance
\cite{konar2019}

% 总的来说，三个水治理稳态之间的先后转变，都是随着流域向社会-水循环发展的过程中先后发生的，存在明显的过渡趋势。
In general, shifts of the three governance regimes occurred sequentially along with a transformation towards the hydro-social cycle.
% 随着不断增强的人类压力在全球普遍逐渐占据主导，这种过渡趋势在社会-生态系统中被认为是普遍存在的，例如生态系统服务和国家经济-社会发展。
This kind of transition may be widespread in socio-ecological systems, such as transition of ecosystem services and transition of economic-social developments, as increasing anthropogenic impacts gradually change the world at large 
\cite{best2020,cummingLinkingEconomicGrowth2018,cummingImplicationsAgriculturalTransitions2014}.
% 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
Regards to water governance we mainly concern, we find that the transition regimes echoes the two kinds of major water governance challenges globally (resource challenges and structural challenges)
\cite{singh2019,porcher2019}.
% 以水资源短缺和供水困难为代表的资源挑战，主要是未开发和正在开发的流域所面临的，与经济和环境变化密切相关。
Resource challenges represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and highly related to economic and environmental changes
\cite{allan2019,florke2018,liu2012}. 
% 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
Other side, highly-controlled and developed basins (especially for transboundary rivers) are mainly facing structural challenges such as water disputes or lack of equity, and in urgent need of flexible and efficient governance structure for social and political aspects
\cite{kitroeff2020,roobavannan2017,unep-dhi2016}.
% 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
It is very representative that resource challenges and structural challenges have occurred successively along the transition of water governance within the YRB, because of rapid-changing regimes.
% 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
Based on that, our analysis suggests that the early stage of transition often leads resource challenges by economic and environmental changes, while the later stage is dominated by structural challenges regarding social and political aspects.
% 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
Aligned with the core dimensions emphasized by UNDP regarding water governance, this schema paints a co-evolution between the governance challenges and basins' transformation towards a hydro-social water cycle, again.
